\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-07 prelims.tex

\myipara{System Assumptions:} We require that $\System$ be forward
deterministic. This requires existence and uniqueness of trajectories
over a finite time horizon $[0,T]$, which can be guaranteed by
Lipschitz continuity of the vector field in each hybrid mode and
ruling away issues such as finite escape
times~\cite{Meiss/2007/Differential}. From a practical standpoint,
these assumptions do not pose significant restrictions for the type of
problems that we wish to address. Finally, we assume full
observability of the system state, validate our results only against
the $\simulate$ function and {\em do not} assume that an analytic
closed-form representation of the system dynamics is available.

As the relations abstract the solution of a continuous time,
foward deterministic hybrid dynamical
system, they are deterministic, causal and satisfy the semi-group property.

From here on, we drop the subscript $\System$.

>>>>

\mypara{System Assumptions:} We require that $\System$ can always be
simulated forward in time with deterministic results. This in turn
requires existence and uniqueness of trajectories over a finite time
horizon $[0,T]$, which can be guaranteed by Lipschitz continuity of
the vector field in each underlying hybrid mode and ruling away issues
such as finite escape times~\cite{Meiss/2007/Differential}.
Furthermore, as the relations abstract the solution of a continuous
time, foward deterministic hybrid dynamical system, they are
deterministic, causal and satisfy the semi-group property.  These
assumptions are justified as for the dynamical systems we address in
this presentation. Finally, we assume full observability of the system
state, validate our results only against the $\simulate$ function (as
the analytic closed-form representation of the system dynamics is
assumed to be unavailable).  From here on, we drop the subscript
$\System$.
